### 2022-12-05 definitions.tex
details

\begin{proof}
We have to show that we can compute a basis of $I^{k+1}$ if we are given a basis of $I^k $. 
Then the
decidability of the stop condition follows directly. Let $B$ be a basis of $I^k$. 
We have
$$I^{k+1} = I \cup pre(I^k ) = I \cup
\bigcup_{s' \in B}
pre(\uparrow \{s' \}).$$
\alain{n'est-ce pas $I^{k+1} = I^k \cup pre(I^k ) = I^k \cup
\bigcup_{s' \in B}
pre(\uparrow \{s' \}).$ ?}
Since $pre(\uparrow \{s' \}$) is computable for any $s'\in S$ by definition, we obtain a finite generating set of $I^{k+1}$ . By
Fact 3, we can compute a basis of $I^{k+1}$.
\end{proof}
\alain{pas de Fact 3}
\subsection{Defining resilience}

@@

\alain{examiner les cas I,J un élement, cloture, tout, clos par le bas et par le haut,... ...}

@@

\begin{theorem}(ref)
{\sc bounded resilience} is decidable for WSTS with strong upward compatibility and effective basis of $post^*$.
\end{theorem}

applications: PN, les automates a pile sont WSTS avec $post^*$ calculable donc resilience calculable. Mais pas ResetPN.

We may generalyse thier result by weakiening the result

\begin{corollary}
{\sc resilience} is decidable for WSTS with strong upward compatibility and effective basis of $post^*$.
\end{corollary}

\begin{proof}
totot
\end{proof}

@@

\begin{proposition}
The hypothesis $post^*$ is undecidable for WSTS with strong upward compatibility.
\end{proposition}

@@

Since Reset Petri nets are also effective WSTS with strong monotony, we could think to use the undecidability of LTL for Reset Petri nets but $Reach \neq \downarrow Reach$.

>>>>

\begin{proof}
We have to show that we can compute a basis of $I^{k+1}$ if we are given a basis of $I^k $. 
Then the
decidability of the stop condition follows directly. Let $B$ be a basis of $I^k$. 
We have
$$I^{k+1} = I \cup pre(I^k ) = I \cup
\bigcup_{s' \in B}
pre(\uparrow \{s' \}).$$
\alain{n'est-ce pas $I^{k+1} = I^k \cup pre(I^k ) = I^k \cup
\bigcup_{s' \in B}
pre(\uparrow \{s' \}).$ ?}
Since $pre(\uparrow \{s' \}$) is computable for any $s'\in S$ by definition, we obtain a finite generating set of $I^{k+1}$ . By
Fact 1, we can compute a basis of $I^{k+1}$.
\end{proof}
\alain{pas de Fact 3}
\subsection{Defining resilience}

@@

\alain{cette dernière propriété fait penser à la $t$-liveness dans un rdPetri ou n'importe quel modèle monotone..qui peut s'exprimer par $ ~ \forall s' \in S ~ (s \rightarrow^* s') \implies \exists s'' \in U_t ~ s' \rightarrow^{*} s''$ ? avec $U_t=\uparrow Pre(t)$=la clôture par le haut des préconditions pour déclencher la transition $t$}
\alain{examiner les cas I,J un élement, cloture, tout, clos par le bas et par le haut,... ...}

@@

\begin{theorem}\cite{DBLP:conf/gg/Ozkan22,DBLP:journals/corr/abs-2108-00889}
{\sc bounded resilience} is decidable for WSTS $S$ with strong upward compatibility and the existence of an algorithm to compute a finite basis of $\uparrow post^*(S)$.
\end{theorem}

\cite{DBLP:conf/gg/Ozkan22} deduced that resilience is decidable for VASS because a finite basis of  $\uparrow post^*$ can be computed.

\begin{corollary}
{\sc resilience} is decidable for context-free grammars and VASS.
\end{corollary}

Context-free grammars and VASS are WSTS avec $\uparrow post^*$ calculable (because the reachability set of a pushdown machine is an effectively computable regular language) is donc resilience calculable.

We may generalyse this last result by strenghthenin to \emph{unbounded} resilience.

\begin{corollary}
{\sc resilience} is decidable for WSTS with strong upward compatibility and effective basis of $\uparrow post^*$.
\end{corollary}

\begin{proof}
The proof is essentially the same than the previous one.
\end{proof}

@@

\begin{proposition}
Given a WSTS with strong upward compatibility, an effective basis of $\uparrow post^*$ is not computable.
\end{proposition}

@@

Since Reset Petri nets are also effective WSTS with strong monotony, we could think to use the undecidability of LTL for Reset Petri nets but $Reach \neq \downarrow Reach$. Another proof could be a reduction of liveness to resilience and liveness is undecidable for many models like reset PN,...
